---
title: "Linear Models"
output: github_document
---

Load key packages and the data.

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

set.seed(1)

```

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood
  ) |> 
  filter(
    borough != "Staten Island"
  ) |> 
  
  select(price, stars, borough, neighborhood, room_type)
```


## Fit some models.

Start relatively simple.

```{r}
fit = lm(price ~ stars, data = nyc_airbnb)

summary(fit)

names(summary(fit))

coef(fit)

fit |> 
  broom::tidy() |> # so we can extract it as a tibble
  select(term, estimate, p.value)


fit |> 
  broom::glance()
```


Try a bit more complex.

```{r}
fit = 
  lm(price ~ stars + borough, data = nyc_airbnb)

fit |> 
  broom::tidy() |> 
  select(term, estimate, p.value) |> 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) |> 
  knitr::kable(digits = 3)
```


## Some diagnostics

(backtrack to some EDA)

```{r}
nyc_airbnb |> 
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  stat_smooth(method = "lm")
```

Most diagnostics use residuals.

```{r}
modelr::add_residuals(nyc_airbnb, fit) |> 
  ggplot(aes(x = borough, y = resid)) + # plot residuals
  geom_violin() +
  ylim(-200, 500)
```

Residuals against stars.

```{r}
modelr::add_residuals(nyc_airbnb, fit) |> 
  ggplot(aes(x = stars, y = resid)) + 
  geom_point()
```

Residuals against fittd valiues.

```{r}
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  modelr::add_predictions(fit) |> 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```

## Hypothesis testing

For single coefficients look at the table.

```{r}
nyc_airbnb = 
  nyc_airbnb |> 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type))

fit = lm(price ~ stars + borough, data = nyc_airbnb)

fit |> 
  broom::tidy()
```

```{r}

fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb)
```

Look at both.

```{r}
fit_null |> 
  broom::tidy()

fit_alt |> 
  broom::tidy()

anova(fit_null, fit_alt) |> 
  broom::tidy()
```

## Do effects differ across boroughs?

First, use a lot of interaction.

```{r}
nyc_airbnb |> 
  lm(price ~ stars * borough + room_type * borough, data = _) |> 
  broom::tidy() # main effect of stars on brooklyn: 27.1-6.14
```

Could just fit separate models.

```{r}
nyc_airbnb |> 
  filter(borough == "Manhattan") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()

nyc_airbnb |> 
  filter(borough == "Brooklyn") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()
```

Get fancy and use list columns.

```{r}
nyc_airbnb |> 
  nest(data = -borough) |> 
  mutate(
    model = map(data, \(x) lm(price ~ stars + room_type, data = x)),
    results = map(model, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results) |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  )
```


What aboutt room type across Manhattan neighborhoods?

```{r}
nyc_airbnb |> 
  filter(borough == "Manhattan",
         neighborhood == "Chinatown") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()

nyc_airbnb |> 
  filter(borough == "Manhattan",
         neighborhood == "Chelsea") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()

manhattan_neighborhood_fit_df =
  nyc_airbnb |> 
  filter(borough == "Manhattan") |> 
  nest(data = -(borough:neighborhood)) |> 
  mutate(
    model = map(data, \(x) lm(price ~ stars + room_type, data = x)),
    results = map(model, broom::tidy)
  ) |> 
  select(neighborhood, results) |> 
  unnest(results)
```

Look at effect of room type.

```{r}
manhattan_neighborhood_fit_df |> 
  filter(str_detect(term, "room_type")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_boxplot()

```


```{r}
manhattan_neighborhood_fit_df |> 
  filter(str_detect(term, "room_type")) |> 
  filter(estimate > 0)

nyc_airbnb |> 
  filter(
    neighborhood == "NoHo",
    room_type == "Shared room"
  )
```


